---
output:
  html_document:
    css: www/styles.css
    anchor_sections: FALSE
    includes:
      in_header: "header_manual.html"

params:
  year_curr: 2025 # Current year of sampling
  all_years: FALSE # If FALSE, only reports on year_curr; TRUE reports on all years
  spp_list: "DB" # If FQAI, matches species in database against OH EPA spp. list. If "DB", matches against tlu_WetlndSpeciesList.    As of 20250606, stick with "DB" until a new FQAI list is published. 
  
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '', scipen = 100)
```

```{r imports, include = FALSE}
library(wetlandHTLN)
library(tidyverse)
library(knitr)
library(kableExtra)
library(DBI)
library(odbc)
#library(htmltools) # for tagList to iterate on a code chunk. Not sure I'm going to need this yet.

importData()
year_curr = params$year_curr
year_range = if(params$all_years == TRUE){2008:year_curr} else {year_curr}
year_hist = 2008:(year_curr-1)
spp_list <- params$spp_list
all_years = params$all_years
#arglist <- list(park = park, years = year)

# locs <- do.call(getPlots, arglist) |>
#   select(LocationID) |> unique() |> c() #|> as.character()
```


Wetland Quality Control checking for CUVA and `r paste(year_curr, collapse = ", ")` {.tabset .tabset-pills}
---

```{r, include = F, results = 'hide'}
source('QC_VIBI_report_compile.R')
```

### QC checks {.tabset}
#### Summary {.tabset}
The table below documents Quality Control checks performed on VIBI-related wetland data, along with number of records returned on each check. If records are returned for a given check, the row is highlighted yellow for errors and blue for records that aren't necessarily errors, but need further review. A separate tab corresponding to each check that returned results by protocol module (e.g. Herbs, Woody, etc.). 
```{r}
QC_check_table
```

#### Sampling Matrix
```{r results = 'asis'}
cat(paste0("The following matrix shows every site sampled ", 
           ifelse(all_years == F, paste0("in ", year_curr, "."), 
                  "across all years."),
           " Highlighted rows are missing data for at least one module."))

tbl_sample_evs
```


```{r eval = loc_include, results = "asis"}
cat("### Locations {.tabset}", "\n\n")

check_null_print(tbl_locid_typos, 4, "LocationID")

check_null_print(tbl_feat_typos, 4, "FeatureType")

check_null_print(tbl_feat_symb, 4, "FeatureID")

check_null_print(tbl_miss_domveg, 4, "DomVeg missing")

check_null_print(tbl_conflict_domveg, 4, "DomVeg conflict")

check_null_print(tbl_area_error, 4, "AreaHA vs TotMods")

check_null_print(tbl_intern_check, 4, "Intern vs TotalMods")

cat("\n\n")

```


```{r eval = pev_include, results = "asis"}
cat("### Sampling Periods/Events {.tabset}", "\n\n")

check_null_print(tbl_miss_periods, 4, "miss PeriodID")

check_null_print(tbl_miss_samp_evs, 4, "miss EventID")

#check_null_print(tbl_no_evs, 4, "No EventIDs") # turned off. Remaining are ORAM visits

check_null_print(tbl_miss_spd, 4, "Miss StartDate")

check_null_print(tbl_odd_dates1, 4, "StartDate1")

check_null_print(tbl_odd_dates2, 4, "StartDate2")

cat("\n\n")

```


```{r eval = herb_include, results = "asis"}
cat("### VIBI Herbs {.tabset}", "\n\n")

check_null_print(tbl_herb_blanks, 4, "Herb blanks")

check_null_print(tbl_herb_locid, 4, "LocationID issues")

check_null_print(tbl_herb_dups, 4, "Duplicate spp.")

check_null_print(tbl_herb_miss, 4, "Missing spp.")

check_null_print(tbl_herb_once, 4, "One-timers")

if(all_years == F){check_null_print(tbl_herb_plot_once, 4, "New to plot")}

cat("\n\n")

```


```{r eval = biomass_include, results = 'asis'}
cat("### VIBI Biomass {.tabset}", "\n\n")

check_null_print(tbl_bmass_blanks, 4, "Biomass blanks")

check_null_print(tbl_non_evs, 4, "Unmatched EventIDs")

check_null_print(tbl_bmass_locid, 4, "LocationID issues")

check_null_print(tbl_bmass_neg, 4, "Negative DryWt_g")

check_null_print(tbl_bmass_dups, 4, "Duplicate DryWt_g")

check_null_print(tbl_wt_99, 4, "DryWt_g 99pct")

```

```{r eval = woody_include, results = "asis"}
cat("### VIBI Woody {.tabset}", "\n\n")

check_null_print(tbl_woody_fid_check, 4, "FeatureIDs")

check_null_print(tbl_woody_blanks, 4, "Woody blanks")

check_null_print(tbl_woody_locid, 4, "LocationID issues")

check_null_print(tbl_woody9s, 4, "-9999 counts")

check_null_print(tbl_diamid_check, 4, "DiamIDs")

check_null_print(tbl_woody_dups, 4, "Duplicate spp.")

check_null_print(tbl_diam_99, 4, "DiamID 99pct")

check_null_print(tbl_count_99, 4, "Counts 99pct")

check_null_print(tbl_woody_miss, 4, "Missing spp.")

check_null_print(tbl_woody_once, 4, "One-timers")

if(all_years == F){check_null_print(tbl_woody_plot_once, 4, "New to plot")}

cat("\n\n")

```

```{r eval = bigt_include, results = "asis"}
cat("### Big Trees {.tabset}", "\n\n")

check_null_print(tbl_woody_comb, 4, "BigTree counts")

check_null_print(tbl_bigt_locid, 4, "LocationID issues")

check_null_print(tbl_bigt_blanks, 4, "BigTree blanks")

check_null_print(tbl_bigt_neg, 4, "Negative DBH")

check_null_print(tbl_dbh_99, 4, "DBH 99pct")

check_null_print(tbl_bigt_miss, 4, "Missing spp.")

check_null_print(tbl_bigt_once, 4, "One-timers")

cat("\n\n")

```

```{r eval = spp_include, results = 'asis'}
cat("### Species List {.tabset}", "\n\n")

#check_null_print(tbl_adv_check, 4, "Adventive check") # doesn't seem like a useful check

check_null_print(tbl_miss_spp, 4, "Unmatched data in tluWSL")

check_null_print(tbl_miss_spp2, 4, "Unmatched tluWSL and FQAI")

cat("\n\n")
```

